\toolname: Property-Based Testing for MPC Security

### 2023-11-03 paper/main.tex

\section{Statistical testing for MPC insecurity}

\subsection{Test algorithm}

@@

We use the techniques from \cite{chalupka2018fast} to build \toolname,
which directly tests for the above conditional dependence without any static analysis of the subject protocol.

@@

The usual trade-offs of significance testing apply.
Setting $\alpha$ too low will cause programs who's insecure-ness is only marginally discernible to the D-Trees
to pass the test.
Setting $\alpha$ higher will compromise one's certainty that a failing program truly is insecure.
There are three reasons why this is not a serious problem with \toolname, each worth considering as its own subtlety.

@@

See Section~\ref{sec:public-repo} for more details.

@@

\section*{Data Availability}\label{sec:public-repo}

TODO.

This section, and everything following, does not count within the body text page limit requirement (so this paper would satisfy a page limit of 1). For your Euro S\&P submission, we expect more useful content than what is in this paper, so you have 13 pages of body text.

>>>>

\section{\toolname: a Statistical Test for Security}

This section describes \toolname, our approach for using statistical independence testing to find security bugs in MPC protocols. The approach is based on the \emph{fast conditional independence test} proposed by Chalupka et al.~\cite{chalupka2018fast}.

\subsection{Conditional Independence Testing by Classification}

Chalupka et al.~\cite{chalupka2018fast} present a high-dimensional conditional independence test based on the observation that if $P(X | Y, Z) = P(X | Y)$ (i.e. $X$ and $Z$ are conditionally independent given $Y$), then $Y$ and $Z$ together will not be more useful for predicting $X$ than $Y$ alone. They leverage this observation to design a test based on training machine learning classifiers: one classifier predicts $X$ from both $Y$ and $Z$, while the other predicts $X$ from $Y$ alone. If the first classifier yields better test error than the second, then the conditional independence property likely does not hold.

\todo{we should maybe introduce decision trees?}

\subsection{The \toolname Algorithm}

@@

We use the techniques from Chalupka et al.~\cite{chalupka2018fast} to build \toolname,
which directly tests for the above conditional dependence without any static analysis of the subject protocol.

@@

The usual trade-offs of significance testing apply.
Setting $\alpha$ too low will cause programs whose insecure-ness is only marginally discernible to the D-Trees
to pass the test.
Setting $\alpha$ higher will compromise one's certainty that a failing program truly is insecure.
There are three reasons why this is not a serious problem with \toolname, each worth considering as its own subtlety.

@@

Our implementation and the code to reproduce our experimental evaluation are available as open-source.\footnote{(Link removed for anonymous submission)}

@@
